% Updated 210719: 1932
\chapter{CONCLUSION AND FUTURE DIRECTION}
\label{ch6}

\section{Overview}
This initial section provides a brief introduction to the concluding chapter. It sets the stage for summarizing the research findings, discussing their implications, and suggesting directions for future work. This overview should serve as a transition from the detailed analysis provided in the previous chapters to the summarization and forward-looking aspects of this final chapter.



\section{Conclusion Of The Study}

This section aims to clearly summarize the main results of your research and bring together your important findings into a final overview. It starts by briefly restating the main outcomes of the study, including a short explanation of the data analysis and results. Then, it focuses on the most important results and data points that directly address the research questions or hypotheses. It also discusses how these key findings are either similar to or different from the ideas and existing research that were mentioned earlier in your work. This helps to show how your results fit into the larger field of study.


\section{Contributions Of The Study}

This section outlines the unique contributions your study makes to its academic discipline or practical field. It starts by emphasizing any new methods you introduced or significant modifications you made to existing methods. Then, it discusses new insights or perspectives your research offers, highlighting how these enhance understanding within the field. Lastly, it describes how your results have expanded the existing body of knowledge, considering both theoretical and practical implications. This part of your study showcases the innovative aspects of your work and its impact on advancing knowledge.

\section{Future Work}

This section discusses the limitations of the current study and suggests directions for future research. It begins by openly addressing the shortcomings and constraints encountered during the research process, such as methodological limitations or data collection challenges. Next, it recommends specific areas where further investigation could yield additional insights, providing concrete suggestions for future researchers. Finally, it outlines strategies for overcoming the limitations identified in this study, suggesting the use of new methodologies, broader datasets, or alternative frameworks to enhance the robustness and scope of future research. This approach not only acknowledges the imperfections of the current study but also paves the way for subsequent advancements in the field.