% Updated 210719: 1932
\chapter{RESULTS}

This chapter presents the empirical outcomes and discusses in detail their significance to the field of study, as well as to the research community. When structuring the results and discussion chapter in an academic or research document, it's crucial to organize the content in a way that clearly presents your findings and interprets their implications. 


\section{Experimental Result}



\subsection{Presentation of Quantitative Data}
Describe and present the findings from the quantitative data through tables, graphs, and statistical analyses. Discuss significant trends or patterns observed in the data.




\subsection{Discussion Of The Results}

Discuss the implications of the results in the context of the existing literature or theories presented in earlier chapters. Interpret what the findings mean for the broader field of study.
Explicitly address how the results relate to each research question or hypothesis stated in the introduction. Discuss whether the findings support or refute the hypotheses.




\section{Qualitative Comparison With Other Studies}

In some cases, you may want to conduct Qualitative Comparison With Other Studies. In this case, you can consider to make a comparison table

\begin{table}[h]
	\centering
	\caption{Comparison of Various Industrial Physics Studies}
	\label{tab:industrialPhysicsCompare}
	\begin{tabular}{lll}
		\toprule[\heavyrulewidth] \toprule[\heavyrulewidth]
		Study & Parameter(s) & Acc (\%)  \\
		\midrule[\heavyrulewidth]
		\cite{Smith2020} & 
		Temperature, Pressure & 
		82.3\\

		\cite{Johnson2019} & 
		Velocity, Turbulence & 
		75.6\\

		\cite{Lee2018} & 
		Power Usage, Operational Hours & 
		89.1\\

		\cite{Kumar2017} & 
		Collision Energy, Particle Type & 
		91.4\\

		\cite{Chen2016} & 
		Frequency, Amplitude & 
		88.7\\

		\cite{Garcia2015} & 
		Chip Thickness, Impurity Levels & 
		84.9\\

		\cite{Morales2014} & 
		Solar Irradiance, Temperature & 
		79.3\\
		
		Proposed Method & 
		Microstructure Analysis, Load & 
		92.5\\ 
		\bottomrule[\heavyrulewidth]
	\end{tabular}
\end{table}






\section{Chapter Summary}

This chapter presents the findings and discussions related to the research questions outlined in the introduction. Initially, it systematically details the results obtained from both quantitative and qualitative analyses, using statistical data, graphical representations, and thematic interpretations to illustrate the key outcomes. Subsequently, the discussion section interprets these results in the context of existing literature, offering a comprehensive analysis of how the findings contribute to the broader field of study.

The chapter addresses each research question thoroughly, identifying whether the evidence supports or challenges the initial hypotheses. It also critically examines the limitations of the study's methodology and the impact these may have on the results. Furthermore, it explores the implications of the findings for future research and practical applications, suggesting directions for further studies and potential improvements in practice. The chapter concludes by summarizing the main findings and their significance, reinforcing the contribution of the study to the existing body of knowledge.
